Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-02 paper.tex
Add paragraph to intro and make second par flow better

Computational fluid dynamics (CFD) presents an attractive method for simulating
cross-flow turbines (CFTs) since it only requires turbulence modeling, i.e., the
machine is described from first principles. However, CFD can be computationally
expensive when done in three dimensions, which may be necessary in some cases.
There are many examples in the literature of 2-D cross-flow turbine simulations
with widely varying results. Balduzzi et al. provides a summary of recent
computations and an attempt to standardize a methodology for using
Reynolds-averaged Navier--Stokes (RANS) to correctly simulate performance of a
2-D CFT \cite{Balduzzi2016}.

>>>>

In the pursuit of a fully sustainable energy profile, cross-flow (often
vertical-axis) turbines (CFTs) still play a role. Despite extensive research and
development in the 1970s through the early 1990s by groups like Sandia National
Labs in the US \cite{Sutherland2012} and the National Research Council in Canada
\cite{Para2002}, the vertical-axis cross-flow Darrieus turbines were all but
abandoned for large scale commercial terrestrial wind power. Today, however,
with the development of marine hydrokinetic (MHK) energy devices, CFTs are at
the forefront, with the first grid-connected commercial device being a
horizontal-axis CFT manufactured and installed by ORPC in Cobscook Bay, Maine
\cite{ORPC2012}. CFTs are also being examined for small-scale onshore wind in
urban areas \cite{Lott2015}, offshore floating wind farms \cite{Paulsen2011,
    Sandia2012}, and onshore wind farms where power output per unit land area is of
interest \cite{Dabiri2011}.

Despite the development of many simple engineering models based on blade element
momentum or vortex modeling, it remains difficult to predict the performance of
cross-flow turbines in all cases---namely when solidity or blade chord to radius
ratio is high, a common characteristic of the smaller CFTs. With computing power
becoming evermore available and affordable, computational fluid dynamics (CFD)
presents an attractive method for simulating cross-flow turbines since it only
requires turbulence modeling, i.e., the machine is described from first
principles. However, CFD can be computationally expensive when done in three
dimensions, which may be necessary in some cases. There are many examples in the
literature of 2-D cross-flow turbine simulations with widely varying results.
Balduzzi et al. provides a summary of recent computations and an attempt to
standardize a methodology for using Reynolds-averaged Navier--Stokes (RANS) to
correctly simulate performance of a 2-D CFT \cite{Balduzzi2016}.
